Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning

### 2018-08-28 paper/paper.tex
paper: latex source clean-up

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\usepackage{graphicx}
\usepackage{hyperref}
%\usepackage{nicefrac}

%\usepackage{caption}
%\usepackage{subcaption}
%\captionsetup{compatibility=false}

% Springer does not support subcaption/caption => use subfig instead and avoid loading the caption package
\usepackage[caption=false]{subfig}

\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{adjustbox}

\usepackage{ upgreek }

\usepackage{xcolor}
\newcommand{\Nora}[1] {\textbf{\textcolor{red}{#1}}}

\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,shadows, shapes.geometric, shapes.misc}
\usepackage[utf8]{inputenc}

\inputencoding{utf8}

@@

%%%%%%%%%%%%%
\newcommand{\todo}[1]{\textbf{\textcolor{red}{TODO: #1}}}
\newcommand{\changed}[1]{\textcolor{purple}{#1}}

\begin{document}
\mainmatter              % start of a contribution
%
% Robust Trajectory Execution
% 
\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}% in Multi-Robot Systems}

% Distributed Real-time Trajectory Replanning for Robust Trajectory Execution
% Robust Trajectory Execution for Distributed Multi-Robot Systems
% Robust Trajectory Execution for Distributed UGV Teams
% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Planning
% Robust Trajectory Execution for Distributed Multi-Robot Teams using Hybrid Real-time Replanning
% Robust Trajectory Execution for Distributed Multi-Robot Teams Using Real-time Replanning

%
\titlerunning{Robust Trajectory Execution for Multi-Robot Teams}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\section{Introduction}
Motion planning for multi-robot systems is particularly important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives such as total energy used~\cite{crazyplanning-ieeetro};
however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.%, as is true in these scenarios.

To compensate for changes in the environment or imperfect execution, one might apply cooperative collision avoidance strategies, such as ORCA~\cite{orca}, at runtime.
However, such algorithms often operate locally and do not take the pre-planned trajectories into account.
Robust trajectory execution, on the other hand, avoids future collision more effectively because it directly considers pre-planned trajectories.
Consider the example in Fig.~\ref{fig:swap2}(a), where two robots must swap positions.
The pre-planned trajectories are collision-free, but they do not consider the newly introduced obstacle and the blue robot does not start at its correct location.
However, the pre-planned trajectories can be used as guidance for replanning.
In this example, robots can get stuck if a local cooperative collision avoidance strategy is applied.
%We propose robust trajectory execution as an extension of cooperative collision avoidance that takes pre-planned trajectories directly into account.
%Our algorithm compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
%Consider the example in Fig.~\ref{fig:swap2}(a), where two robots have to swap their positions.
%Although the pre-planned trajectories are collision-free, they do not consider the new obstacle and the blue robot does not start at its correct location.
Using our method, the robots can successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense other robots' positions and the obstacles around them.

\begin{figure}
%\centering
%\subfloat[Initial configuration and pre-planned trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
%\label{fig:swap2:initial}
%}
\hfill
%\subfloat[Final configuration and executed trajectories.]{
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
%\label{fig:swap2:final}
%}
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_initial.pdf}
%\caption{Initial configuration.}
%\label{fig:swap2:initial}
%\end{subfigure} \hfill
%\begin{subfigure}[t]{0.48\textwidth}
%\centering
%\includegraphics[width=1.0\textwidth]{images/swap2_final.pdf}
%\caption{Final configuration and executed trajectories.}
%\label{fig:swap2:final}
%\end{subfigure}
\caption{(a) Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines).
The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
(b) Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory.
}
\label{fig:swap2}
\end{figure}

Robust trajectory execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
Our method relies on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.
%We also apply our dynamic receding horizon approach to ORCA and show that it helps to avoid deadlocks more effectively in that case, although the ORCA-based solution does not support higher-order dynamic limits.

% The contributions of this work are
The main contribution of this work is a novel distributed algorithm for robust trajectory execution that considers higher-order dynamic limits.
It also compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
%It also compensates for environmental changes and imperfect trajectory execution.
We show in simulations that our method avoids deadlocks better than ORCA~\cite{orca}.
Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.

%\todo{perhaps write some more about what experiments we did, after we have the material}

% \begin{tabular}{l||l}
% \hline % global
% $m$ & number of robots\\
% $n$ & problem dimension\\
% $c$ & order of derivative up to which smoothness is required \\
% $\gamma_k$ & dynamic limit of each robot for the $k\th$ derivative of its trajectory\\
% %$\Gamma_k$ & \\
% %$r_s$ & radius\\
% $R(\vp), r_s$ & space that robot occupies at position $\vp$ (sphere with radius $r_s$)\\
% $\psi$ & current time\\
% $\uptheta, \uptheta'$ & number of static obstacles\\
% \hline % per robot
% $\vo_i(t), t\in[0, T_i]$     &  original trajectory of robot $i$\\
% $\vp_i(t)$ & position of robot $i$ at time $t$\\
% $\cO_i$ & obstacles\\
% %$\vf_i(t)$ & \\
% $\cV_i$ & voronoi cell\\
% $\cS_i^j$ & \\
% $\cH_i^j, \valpha_i^j, \beta_i^j$ & hyperplane robot-robot\\
% $M_j^b$ & hyperplane robot-obstacle\\
% %$H$, $A$, $lbA$, $ubA$, $g$ & QP\\
% $K$ & iteration\\
% \hline % algorithm
% $l$ & pieces\\
% $d$ & degree\\
% $\lambda_i, \theta_j$ & QP\\
% $\tau, \tau'$ & \\
% $\delta t$ & \\
% $\vf^{K}_i(t)$ & duration $T^{K}_i$ \\
% $\vf^{K}_{i,j}(t), t\in[0, T^{K}_{i,j}]$ & $j\th$ piece\\
% $\vP^{K}_{i,j,\rho}$ & denotes the $\rho\th$ control point\\
% \end{tabular}

\section{Related Work}
\label{sec:relatedWork}

% Our method is closely related to cooperative collision avoidance.
% Such approaches assume that all robots follow the same strategy and can provide formal collision avoidance guarantees.
% They typically find a subset of the configuration or control space that is safe to occupy for some time horizon.
% A local planner can then optimize an arbitrary function as long as the robots stay in their respective safe configuration spaces.
% Recent cooperative collision avoidance approaches include reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
%Many extensions of the RVO method have been proposed to support different kinds of robots, including heterogeneous teams, see \cite{epsilonCCA} for an extensive overview.
Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
Safety barrier certificates achieve collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
%The three approaches are decentralized and require only position (BVC and safety barrier certificates) or position and velocity estimates (RVO) of their neighbors.
Our robust trajectory execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)

%Our real-time planning is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro}.
%Here, a map of the environment, the specification of the robots, and the robots' start and goal locations are given.
%The goal is to find smooth, collision-free trajectories that approximately minimize the total energy used.
%The offline planner works in two stages: first, a discrete solution (on a discrete roadmap) is found using a graph search. Second, a quadratic program computes smooth trajectories for each robot, using the discrete result to define constraints and an initial solution.
Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
Similar to previous work we use discrete search to quickly get out of local minima, but do so in a distributed manner.

While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
%Polynomial trajectories can be generated using a QP~\cite{richterISRR} without taking obstacles directly into account.
%QP-based formulations on B-splines or B\'ezier curves have been used to consider obstacles in form of linear hard constraints~\cite{flores,tang}.
%In this case a unconstrained QP formulation might be used, but obstacles cannot be directly taken into account.
%Other basis functions, such as B-splines, allow us to add obstacles as linear hard constraints in a quadratic program~\cite{flores,tang}.
Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
%and therefore guarantees collision-free execution (or easy error-case detection in case our quadratic program is infeasible).
The optimization can use a discrete plan as an initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.

% multi-robot:
% BVC, RVO, barrier certificate

% stanford paper

% tu munich paper
%\cite{replanning-usenko}

% t-ro paper (& other traj opt papers)
%\cite{crazyplanning-ieeetro}
%\cite{tang}
%\cite{flores}

% other traj opt:
%\cite{replanning-eth}
%\cite{richterISRR}

\section{Problem Formulation} \label{problemFormulation}
% assumptions: circular robots; robots follow the same rules; static (or slow) obstacles
% input: original curves; positions of peers; dynamic limits; environment (at least able to sense); dt; curve_count; T
% output: at each dt: new trajectory such that there is no collision (guaranteed)
% issues: no live-lock guarantee
The general problem we would like to solve can be formulated as follows. 
Consider a group of $m$ robots. Each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory $(\R\to \R^n)$ of $i\th$ robot where time } t\in[0,T_i],\\
    %ct&:\text{ current global time},\\
    %\delta t&:\text{ replanning period},\\
    %\tau&: \text{time horizon},\\ 
    c&:\text{ order of derivative up to which smoothness is required},\\
    %\cO&:\text{ free space representation of the environment},\\
    %\{\vp_i\}&:\text{ set of positions of all robots},\\
    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\ %(we use a sphere with }
     %     & \text{radius $r_s$, but $R(\vp)$ can be any convex shape), and}\\
    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.%\\
    %&\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
\end{align*}

Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of other robots as well as the current occupied space $\cO_i$ around it\footnote{Since our approach can accommodate many sensing modalities, we do not provide a specific sensing capability in the general problem.}.
We represent $\cO_i$ as a set of $\uptheta$ convex obstacles.
%, which can be achieved in practice by using data structures such as an OctoMap~\cite{octomap} \Nora{What can be achieved? sensing them? or knowing them? or the representation?}.
Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
%Each robot can sense the position of their neighbors, but robots cannot communicate with each other.
Each robot $i$ must execute a trajectory $\vf_i(t)$, where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision-free, and}\\ 
    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We solve this problem approximately, using a dynamic receding horizon approach iteratively.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to the user-provided period $\delta t$.
We set $R(\vp)$ to a sphere with radius $r_s$ centered at $\vp$.
%We adjust the planning horizon of $\vf^{K}_i(t)$ dynamically to avoid local minima.

%\todo{add paragraph about how we actually (approximately solve this problem)}

% \begin{align*}
%     \text{Given,}\ \ \ \ \ &\\
%     \vo^i(t')&:\text{ original trajectory of robot $i$},\\
%     ct&:\text{ current global time},\\
%     \delta t&:\text{ replanning period},\\
%     \tau&: \text{time horizon},\\ 
%     c&:\text{ maximum continuity between pieces},\\
%     \cO&:\text{ free space representation of the environment},\\
%     \{\vp_i\}&:\text{ set of positions of all robots},\\
%     \gamma&: \text{ dynamic limits of robots in any derivation degree},\\
%     &\ \ \ \ \gamma_j \text{ being the limit for $j\th$ derivation degree}\\
%     \text{find a new}&\text{ trajectory $\vf^{i,K}(t)$ such that},\\
%     \vf^{i,K}(t)&\text{ is}\text{ continuous up to degree $c$ for }t\in [0,\tau],\\
%     \frac{d^j\vf^{i,K}}{dt^j}(0) &= \frac{d^j\vf^{i,K-1}}{dt^j}(\delta t)\text{ for } j\in\{0,1,...,c\}\\
%     \vf^{i,K}(t)&\text{ is collision free for $t\in [0,\delta t]$},\\
%     \vf^{i,K}(t)&\text{ tracks $\vo^i(t')$ as close as possible for $t\in[0,\tau]$ or equivalently $t'\in[ct, ct+\tau]$ }, \text{and}\\
%     \left\|\frac{d^j \vf^{i,K}(t)}{dt^j}\right\| &\leq \gamma_j\text{ for } t\in [0,\tau],\\
% \end{align*}

\section{Preliminaries}

This section introduces important mathematical concepts and notations that will be used throughout the paper.

@@

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ bounded by hyperplane $\cH_i^j$ that separates point $\vp_i$ from $\vp_j$. $\cH_i^j$ has normal $\valpha_i^j \in \R^n$ and distance $\beta_i^j\in \R$ along $\valpha_i^j$ such that
\begin{equation}
    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s.
    \label{voronoiAlphaBeta}
\end{equation}
% \begin{align}
%     \valpha_i^j &= \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|}\label{voronoiAlpha}\\
%     \beta_i^j &= \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s. \label{voronoiBeta}
% \end{align}

% The set of all buffered Voronoi cells is called the buffered Voronoi decomposition of the space.
For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside of at most one of the buffered Voronoi cells.
We use this property in order to avoid robot-to-robot collisions.

@@

% \begin{align}
%     \cS_i^j = \left\{\vp : \valpha_i^j \cdot \vp - \beta_i^j \leq 0\right\}
% \end{align}

% Using this definition, an equivalent definition for the set \eqref{voronoi_cell_definition} is
% \begin{align}
%     \cV_i = \bigcap\limits_{j\neq i} \cS_i^j \label{voronoiEquation}.
% \end{align}
Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.

@@

The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein};
%This is called the \emph{convex hull property of B\'ezier curves}.
we leverage this property to avoid robot-to-obstacle collisions.

@@

% \subsection{Support Vector Machine}\label{svmSection}
% A support vector machine is a supervised learning method that is used to classify data into several classes.
% In binary classification problems, we are given a linearly separable data set $\{(\vx_i, y_i)\}$ where $\vx_i \in \R^n$ is a data point and $y_i \in \{-1, 1\}$ is the corresponding class label.
% The goal is to find a hyperplane with normal $\vw$ and distance along the normal $\frac{b}{\|w\|}$ that separates the two classes.
% The SVM problem for binary classification with a separable data set can be stated as the following quadratic optimization problem with hard constraints \cite{SVM}:
% \begin{align*}
%     \text{minimize}\ \ \  &\|\vw\|\\
%     \text{subject to}\ \ \  & y_i(\vw \cdot \vx_i - b) \geq 1
% \end{align*}
% We use SVMs to define collision free convex subspaces that are obstacle-free.

\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
Our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
The decision variables $\vx$ are the concatenated B\'ezier curve control points.
The overall structure of our quadratic optimization problem is as follows:
\begin{align}
\begin{split}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
    % &\vlb \leq \vx \leq \vub
\end{split}
\end{align}
%, while bounds on variables are represented with vectors the $\vlb$ and the $\vub$.

@@

% There are three types of constraints we impose on the curves: \emph{initial point constraints}, \emph{continuity constraints}, and \emph{hyperspace constraints}.

% \begin{description}
% \item [Initial Point Constraints]
% An initial point constraint on a B\'ezier curve requires the first control point of the curve to be equal to a given vector.
% This requires $n$ linear constraints on the control points. %, $n$ being the dimension we are working in.

% \item[Continuity Constraints]
% A continuity constraint between curve $j$ and curve $j+1$ requires curve $j$ at the end to be equal to the curve $j+1$ at the beginning in any order of derivation.
% We take the vector difference of those values and require it to be equal to $\vzero$.
% This requires $n$ linear constraints on the control points.

% \item[Hyperspace Constraints]
% A hyperspace constraint requires all points of a curve to be on a specific side of a hyperplane.
% Given a hyperplane with normal $\vn$ and distance along the normal $b$, the hyperspace constraint requires one linear constraint for each relevant control point.
% \end{description}

% The construction of the QP is discussed in more detail in previous work~\cite{crazyplanning-ieeetro}.

\section{Approach}

% TODO: running example?

%\subsection{Approach Overview}
Replanning is done at a fixed period of $\delta t$.
In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory \changed{$\vf^K_i(t)$}.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.

% In each planning iteration $K$ that corresponds to the current time $\psi$, we sense the neighbors' positions and compute the buffered Voronoi cell $\cV_i$.
% We also assume that we have a current representation of the occupied space ($\cO_i$). Even if we use the complete occupation map in our examples, our method also works for local maps which can be constructed in practice by using LIDAR or RGB-D sensors.

%The trajectory $f^K_i(t)$ is safe to execute at least up to time $\delta t$, and minimizes the deviation from the original trajectory $o_i(t)$.

@@

    \draw [dotted] (c9) -- (c10);
    \draw [dotted] (c10) -- (c12);
    \draw [dotted] (c12) -- (c11);
    \draw [dotted] (c11) -- (c9);
\end{tikzpicture}
}
%\end{adjustbox}
\caption{Overview of the replanning pipeline.
}
\label{fig:flowchart}
\end{figure}

%\todo{DISCUSS: planning/execution overlap?}

\subsection{Discrete Planning} \label{discretePlanning}

>>>>

@@

\usepackage{graphicx}
\usepackage{hyperref}

\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{adjustbox}
\usepackage{upgreek}
\usepackage{xcolor}
\usetikzlibrary{arrows, arrows.meta, fit, positioning, quotes,shadows, shapes.geometric, shapes.misc}
\usepackage[utf8]{inputenc}
\inputencoding{utf8}

@@

\begin{document}
\mainmatter              % start of a contribution
\title{Robust Trajectory Execution for Multi-Robot Teams Using Distributed Real-time Replanning}
\titlerunning{Robust Trajectory Execution for Multi-Robot Teams}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Baskın Şenbaşlar \and Wolfgang H\"onig \and
Nora Ayanian}
%
%\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Baskın Şenbaşlar, Wolfgang H\"onig, Nora Ayanian}
%
\institute{University of Southern California, Los Angeles CA, USA,\\
\email{\{baskin.senbaslar, whoenig, ayanian\}@usc.edu}}

@@

\section{Introduction}
Motion planning for multi-robot systems is particularly important in cases where many robots must interact with each other in confined spaces, potentially with many obstacles.
Examples include coordination of robots in warehouses~\cite{Kiva}, traffic management at intersections~\cite{IntersectionManagementDresner}, and airport management~\cite{AirportTug}.
Modern planning algorithms can find trajectories that effectively coordinate hundreds of robots while approximately optimizing objectives such as total energy used~\cite{crazyplanning-ieeetro};
however, all such solutions assume that the resulting trajectories can be executed nearly perfectly, which is an unrealistic assumption for teams of hundreds of robots that must operate persistently.

To compensate for changes in the environment or imperfect execution, one might apply cooperative collision avoidance strategies, such as ORCA~\cite{orca}, at runtime.
However, such algorithms often operate locally and do not take the pre-planned trajectories into account.
Robust trajectory execution, on the other hand, avoids future collision more effectively because it directly considers pre-planned trajectories.
Consider the example in Fig.~\ref{fig:swap2}(a), where two robots must swap positions.
The pre-planned trajectories are collision-free, but they do not consider the newly introduced obstacle and the blue robot does not start at its correct location.
However, the pre-planned trajectories can be used as guidance for replanning.
In this example, robots can get stuck if a local cooperative collision avoidance strategy is applied.
Using our method, the robots can successfully swap positions, while staying as close as possible to the pre-planned trajectories, as in Fig.~\ref{fig:swap2}(b).
Our method is fully distributed and requires no communication. The robots only need to know their own trajectories and be able to sense other robots' positions and the obstacles around them.

\begin{figure}
\includegraphics[width=0.45\textwidth]{images/swap2_initial.pdf}
\hfill
\includegraphics[width=0.45\textwidth]{images/swap2_final.pdf}
\caption{(a) Two robots (green and blue circles) are tasked with following their pre-planned trajectories (green and blue dashed lines).
The initial plans were created without the knowledge of the obstacle (gray) and the blue robot does not start at its planned initial position.
(b) Our approach computes smooth trajectories in real-time, avoiding both the new obstacle and other robots while staying close to the pre-planned trajectory.
}
\label{fig:swap2}
\end{figure}

Robust trajectory execution is an extension of cooperative collision avoidance where the objective is to stay as close to the originally planned trajectories as possible.
In contrast, traditional collision avoidance methods frequently only take a desired velocity, desired goal state, or desired action as input (we discuss these in more detail in Section~\ref{sec:relatedWork}).
Our method relies on \emph{Buffered Voronoi Cells} (BVC)~\cite{bufferedVoronoiCells} as the underlying cooperative collision avoidance strategy and retains the same theoretical guarantees.
We employ a novel combination of trajectory optimization and discrete search-based planning using a dynamic receding horizon approach.
The discrete search allows us to avoid local minima effectively even in difficult scenarios, while the trajectory optimization generates smooth trajectories that are collision-free.

The main contribution of this work is a novel distributed algorithm for robust trajectory execution that considers higher-order dynamic limits.
It also compensates for a variety of dynamic changes, including imperfect motion execution of robots, newly appearing obstacles, robots breaking down, or external disturbances.
We show in simulations that our method avoids deadlocks better than ORCA~\cite{orca}.
Furthermore, we implement and test our approach on a team of six differential drive robots with several dynamic environmental changes.

\section{Related Work}
\label{sec:relatedWork}
Our method is closely related to cooperative collision avoidance such as reciprocal velocity obstacles, buffered Voronoi cells, and safety barrier certificates.
Methods based on reciprocal velocity obstacles (RVO)~\cite{RVO} assume that robots continue with constant velocity and compute the safe configuration space such that no other robot might collide for the time horizon.
Many extensions of the RVO method have been proposed, see \cite{epsilonCCA} for an extensive overview.
Buffered Voronoi Cells (BVC)~\cite{bufferedVoronoiCells} compute the safe configuration space for a robot by its Voronoi cell shifted by the physical extent of the robot. 
Safety barrier certificates achieve collision-free operation by modifying a user-specified controller such that no collision can occur~\cite{barrierCertificates}.
Our robust trajectory execution approach uses cooperative collision avoidance at its core (specifically BVC), while extending it to minimize the difference to the original trajectories (rather than just a preferred velocity as in \cite{epsilonCCA}, preferred control input as in \cite{barrierCertificates}, or difference over a fixed time horizon as in \cite{bufferedVoronoiCells}.)

Our method is inspired by our previous work on offline planning for robotic teams~\cite{crazyplanning-ieeetro} and uses the same optimization framework based on B\'ezier curves to generate trajectories, although with a different cost function.
Similar to previous work we use discrete search to quickly get out of local minima, but do so in a distributed manner.

While our approach naturally works in multi-robot settings, some of the methods are inspired by single-robot optimization and collision avoidance.
Local collision avoidance for single robots such as UAVs can be formulated as optimization problems~\cite{replanning-eth,replanning-usenko}.
In both cases collisions are considered as a soft constraint in the cost function using a Euclidean (Signed) Distance Field.
In contrast, our formulation uses a hard constraint allowing us to easily detect infeasible trajectories.
The optimization can use a discrete plan as an initial guess~\cite{replanning-eth} or shift the existing trajectory based on newly appearing obstacles~\cite{replanning-usenko}.
In contrast, our approach shifts the existing trajectory whenever possible, while falling back to an efficient discrete planner with dynamic receding horizon to avoid local minima.

\section{Problem Formulation} \label{problemFormulation}
The general problem we would like to solve can be formulated as follows. 
Consider a group of $m$ robots. Each robot $i$ is given the following:
\begin{align*}
    \vo_i(t)&:\text{ original trajectory $(\R\to \R^n)$ of $i\th$ robot where time } t\in[0,T_i],\\
    c&:\text{ order of derivative up to which smoothness is required},\\
    R(\vp)&:\text{ convex collision shape of any robot at position $\vp$},\\
    \gamma_k&: \text{ dynamic limit of the robot for the $k\th$ derivative of its trajectory}.
\end{align*}

Each robot $i$ can sense the positions $\{\vp_1,\ldots,\vp_m\}$ of other robots as well as the current occupied space $\cO_i$ around it\footnote{Since our approach can accommodate many sensing modalities, we do not provide a specific sensing capability in the general problem.}.
We represent $\cO_i$ as a set of $\uptheta$ convex obstacles.
Robots are unaware of the other robots' planned trajectories, and cannot communicate with each other.
Each robot $i$ must execute a trajectory $\vf_i(t)$, where $\vf_i(t)$ is a solution to the following optimization problem:
\begin{align}
\begin{split}
    \text{minimize } & \int_{0}^{T_i}\left\|\vf_i(t)-\vo_i(t)\right\|^2 dt\\
    \text{subject to }& \\
    &\vf_i(t) \text{ is}\text{ continuous up to degree $c$},\\
    &\frac{d^j\vf_i}{dt^j}(0) = \frac{d^j\vp_i}{dt^j}(0)\text{ for } j\in\{0,1,...,c\}\\
    &\vf_i(t)\text{ is collision-free, and}\\ 
    &\left\|\frac{d^k \vf_i(t)}{dt^k}\right\| \leq \gamma_k\text{ for all desired $k$},\\
    \text{where } & t\in [0,T_i].
\end{split}
\label{eq:problem:opt}
\end{align}

We solve this problem approximately, using a dynamic receding horizon approach iteratively.
At every iteration $K$, robot $i$ plans a trajectory $\vf^{K}_i(t)$ that starts at the robots' current position and is safe to execute up to the user-provided period $\delta t$.
We set $R(\vp)$ to a sphere with radius $r_s$ centered at $\vp$.

\section{Preliminaries}
This section introduces important mathematical concepts and notations that will be used throughout the paper.

@@

The inequality inside \eqref{voronoi_cell_definition} defines a hyperspace $\cS_i^j$ bounded by hyperplane $\cH_i^j$ that separates point $\vp_i$ from $\vp_j$. $\cH_i^j$ has normal $\valpha_i^j \in \R^n$ and distance $\beta_i^j\in \R$ along $\valpha_i^j$ such that
\begin{equation}
    \valpha_i^j = \frac{\vp_j - \vp_i}{\|\vp_j-\vp_i\|} \text{ and }
    \beta_i^j = \valpha_i^j \cdot \left(\frac{\vp_i + \vp_j}{2}\right) - r_s.
    \label{voronoiAlphaBeta}
\end{equation}

For a given buffered Voronoi decomposition of the space, any point $\vp\in \R^n$ can be inside of at most one of the buffered Voronoi cells.
We use this property in order to avoid robot-to-robot collisions.

@@

Thus, we can compute the buffered Voronoi cell of any robot $i$ as the set of the hyperplanes $\cH_i^j$ in $O(m)$ time.

@@

The curve starts at $\vP_0$ and ends at $\vP_d$, however does not interpolate other control points.
A B\'ezier curve lies completely inside the convex hull of its control points~\cite{Bernstein};
we leverage this property to avoid robot-to-obstacle collisions.

@@

\subsection{Trajectory Optimization using Quadratic Programming} \label{trajectoryOptimization}
Our replanning approach utilizes \emph{quadratic programming} (QP) for trajectory optimization.
The decision variables $\vx$ are the concatenated B\'ezier curve control points.
The overall structure of our quadratic optimization problem is as follows:
\begin{align}
\begin{split}
    \text{minimize}\ \ \ &\frac{1}{2}\vx^TH\vx + \vx^T\vg\\
    \text{subject to}\ \ \ & \vlbA \leq A\vx \leq \vubA.
\end{split}
\end{align}

@@

\section{Approach}
Replanning is done at a fixed period of $\delta t$.
In each iteration $K$, we sense the other robots' positions to compute the buffered Voronoi cell $\cV_i$, update our current representation of the occupied space ($\cO_i$), and compute a trajectory $\vf^K_i(t)$.
The planning horizon $\tau'$ is automatically adjusted, but the desired planning horizon $\tau$ can be provided.

@@

    \draw [dotted] (c9) -- (c10);
    \draw [dotted] (c10) -- (c12);
    \draw [dotted] (c12) -- (c11);
    \draw [dotted] (c11) -- (c9);
\end{tikzpicture}
}
\caption{Overview of the replanning pipeline.
}
\label{fig:flowchart}
\end{figure}
